Nanophotonic Computational Design

### 2013-02-18 defense/pres2.tex
Getting there with presentation remake.
Minor.
Getting there...

\input defs.tex
\raggedright
\special{! TeXDict begin /landplus90{true}store end }
\renewcommand{\oursection}[1]{
\foilhead[-1.0cm]{#1}
}
\newcommand{\myfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=6.5cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\medfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=10cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\bigfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=12cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\BI}{\begin{itemize}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{itemize}}

@@

\vfill
\newpage

Goal: Show you how to design \emph{any} linear nanophotonic device
\myfig{takeaway}

\pause
\BI Physics Advisory: 
    \begin{quote}CONTAINS INVOLVED MATHEMATICAL CONTENT\end{quote}

\pause
\I  Math Advisory: 
    \begin{quote}CONTAINS INVOLVED NANOPHOTONIC CONTENT\end{quote}
\vfill
\newpage

\oursection{Given a field, can we find its structure?}
\myfig{thedefinition}
\I  Electromagnetic wave equation 
    ($\text{field}\to E$, $\text{structure}\to\epsilon$)
    \BE \nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E = 
        -i \omega J \EE

>>>>

\input defs.tex
\raggedright
\special{! TeXDict begin /landplus90{true}store end }
\newcommand{\nextpage}{\vfill\newpage}
\renewcommand{\oursection}[1]{
\foilhead[-1.0cm]{#1}
}
\newcommand{\myfig}[2]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=#2cm]{fig/#1.jpg}}
    \end{figure}
}

\newcommand{\smallfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=6.5cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\medfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=10cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\bigfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=12cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\BI}{\begin{itemize}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{itemize}}

@@

\nextpage

Goal: Show you how to design \emph{any} linear nanophotonic device
\smallfig{takeaway}
\pause
\BI Device properties: 
    \BI Full 3D
    \I  Compact
    \I  Efficient
    \I  Multi-mode 
    \I  Multi-functional \EI
\nextpage

\I  Developed by
    \BI applying (convex) optimization techniques (math)
    \I  to the area of nanophotonics (physics)
    \I  and implementing in software (programming) \EI
\pause
\I  Physics Advisory: 
    \begin{quote}CONTAINS INVOLVED MATHEMATICAL CONTENT\end{quote}
\pause
\I  Math Advisory: 
    \begin{quote}CONTAINS INVOLVED NANOPHOTONIC CONTENT\end{quote}
\nextpage

\oursection{Given a field, can we find its structure?}
\smallfig{my_definition}
\stepwise{
\step{\I  Equivalently, find $\epsilon$ (structure) given $E$ (field)
    \BE \nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E = 
        -i \omega J \EE}
\step{\I  If possible, we can design \emph{any} nanophotonic/optical component!}
}
\nextpage

\I Answer: Yes, given $E$ we \emph{can} solve for $\epsilon$ (trivial!)
    \stepwise{
    \begin{align*} 
    \nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E &= 
        -i \omega J \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\\
    \step{\omega^2 \epsilon E &= \nabla\times\mu_0^{-1}\nabla\times E + 
        i \omega J }\\
    \step{\omega^2 E \epsilon &= \nabla\times\mu_0^{-1}\nabla\times E + 
        i \omega J }\\
    \step{\epsilon &= (\nabla\times\mu_0^{-1}\nabla\times E + 
        i \omega J)/ \omega^2 E} 
    \end{align*}
    }
\I  Solving for $\epsilon$ actually way faster than simulation (solving for $E$)!
\nextpage

\I  Obvious and well-known from a mathematical perspective
    \BI Pre-requisite (200-level) class in optimization curriculum
    \I  Not yet taught (I think) in optics/photonics at Stanford \EI
    \stepwise{\step{
    \BE
    \underbrace{\nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E = 
                -i \omega J }_\text{physics}
    \quad\longrightarrow\quad
    \underbrace{A(z)x = b}_\text{linear algebra}
    \EE
    \begin{align*}
    E &\to x \\
    \epsilon &\to z \\
    \nabla\times\mu_0^{-1}\nabla\times - \omega^2 \epsilon &\to A(z) \\
    -i\omega J &\to b
    \end{align*}
    }
\step{\I  Key: If $A(z)$ is linear in $z$ then $A(z)x=b$ is as well!}
    }
